---
title: "Node analysis of social connectedness and health inequalities"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

Following up on our discussion last week, we now look at five things specifically:

1. Reduce multicollinearity by using just one SCI variable and no interactions
2. Adding countries not as random, but fixed effects
3. Consider moving to multi-level modelling
4. Avoid overfitting by using the HDI as the only control (besides SCI and countries)
5. Focus on outcomes related to sexual and reproductive health. This means dropping child vaccination outcomes and adding outcomes on knowledge and behaviour related to HIV and FGM

### Relevant libraries

```{r message=FALSE, warning=FALSE}
library(tidyverse)    # Data wrangling
library(sf)           # Spatial analysis
library(caret)        # For machine learning and preprocessing
library(spdep)        # For spatial analysis
library(spatialreg)   # For spatial regressions
library(olsrr)        # For OLS residual diagnostics
library(lme4)         # For random effects models
library(lmerTest)     # For approximated p-values in mixed models
library(ggplot2)      # Visualizations
library(broom)        # For data.frame-like summary outputs
library(survey)        # For weighted modelling

library(sjPlot)       # for tab_model function

library(stargazer)   # for latex output

select <- dplyr::select
```

### Relevant data

```{r message=FALSE, warning=FALSE}
# Map data
afr_dat <- st_read(dsn = "/Users/tillkoebe/Documents/GitHub/health_inequalities/combined_dataset/GADM_1_geometries.gpkg") %>% 
  st_make_valid() %>% 
  st_transform(4326)

# Social Connectedness Index
sci <- read.csv("/Users/tillkoebe/Documents/GitHub/health_inequalities/external_dataset/sci_indices.csv") %>% 
  distinct(user_loc, .keep_all = T)

# Worldpop covariates
wp <- read.csv("/Users/tillkoebe/Documents/GitHub/health_inequalities/external_dataset/wp.csv") %>% 
  distinct(GID_1, .keep_all = T)

# Human Development Index
hdi <- read.csv("/Users/tillkoebe/Documents/GitHub/health_inequalities/external_dataset/hdi.csv") %>% 
  distinct(GID_1, .keep_all = T)

# Facebook covariates
fb <- read.csv("/Users/tillkoebe/Documents/GitHub/health_inequalities/external_dataset/fb.csv") %>% 
  distinct(GID_1, .keep_all = T)

# DHS data
dhs <- read.csv('/Users/tillkoebe/Documents/GitHub/health_inequalities/external_dataset/dhs_health_individual.csv')

# DHS aggregate data
dhs_agg <- read.csv('/Users/tillkoebe/Documents/GitHub/health_inequalities/external_dataset/dhs_health.csv')

# Afrobarometer
afr <- read.csv('/Users/tillkoebe/Documents/GitHub/health_inequalities/external_dataset/afrobarometer.csv') %>% 
  distinct(GID_1, .keep_all = T)

# Centrality measures
sci_cen <- read.csv('/Users/tillkoebe/Documents/GitHub/health_inequalities/external_dataset/all_centrality_measures.csv') %>% 
  rename(GID_1 = user_loc)

```
### Defining targets and controls

Let's define our targets and controls:
```{r}
### Define targets
dhs_targets <- dhs %>% 
  select(fp_use_mod, hk_cond_notprtnr, hk_test_ever, fp_know_mod, 
         hk_knw_linear_index, hk_knw_any, hk_knw_comphsv) %>% 
  # select(fp_use_mod, hk_cond_notprtnr) %>% #excluded as they either reduce sample size or they are out of the 0-1 range
  # select(fp_know_any, fp_know_mod, hk_ever_heard, hk_knw_risk_sex, hk_knw_risk_cond) %>% 
  names()

### Define controls
dhs_controls <- c(
  'v104', # gender
  'v012', # age
  'v025', # urban/rural
  'v106', # highest educational level
  'v243a', # mobile phone ownership
  'v270' # wealth index by quintiles
  # "hk_knw_linear_index",
  # "hk_knw_any",
  # "hk_knw_comphsv"
)

sci_controls <- c('Mean_dist_to_SCI_km', # Average distance of friendships
                  'Median_dist_to_SCI_km', # Average distance of friendships
                  'Std_dist_to_SCI_km', # Clustering measure of friendships across distances
                  'Total_dist_to_SCI_km', # Total distance of friendships
                  'Ratio_selfloop_to_country', # Share of local friendships within the same country
                  'Ratio_selfloop_to_africa', # Share of local friendships that stay within Africa
                  'Ratio_selfloop_to_all_sci', # Share of local friendships of all friendships
                  'Average_distance_of_friendships_km', 
                  'Mean_SCI_without_Self', # Average probability of friendships with other regions
                  'Median_SCI_without_Self', # Average probability of friendships with other regions
                  'Std_SCI_without_Self', # Clustering measure for the probability of friendships with other regions
                  'Mean_SCI_with_Self', # Average probability of friendships across all regions
                  'Median_SCI_with_Self', # Average probability of friendships across all regions
                  'Std_SCI_with_Self', # Average probability of friendships across all regions
                  'Mean_friendship', # Average friendships per FB users
                  'Median_friendship', # Average friendships per FB users
                  'Std_friendship', # Clustering measure for friendships per FB user
                  'Total_friendship', # Sum of friendships per FB user 
                  'Ratio_SCI_low_hi_africa', # Share of friendships to regions with a low health index
                  'Ratio_SCI_middle_hi_africa', # Share of friendships to regions with a medium health index
                  'Ratio_SCI_high_hi_africa' # Share of friendships to regions with a high health index
)

hdi_controls <- c('HDI')

wp_controls <- c(
  'Mean_of_Night_Light',
  'Std_of_Night_Light',
  'Mean_distance_to_major_rd_intersection',
  'Std_distance_to_major_rd_intersection',
  'Mean_distance_to_major_rd',
  'Std_distance_to_major_rd',
  "Mean_distance_to_inland_water",
  "Std_distance_to_inland_water",
  "Mean_built_settlement_growth",
  "Std_built_settlement_growth")

fb_controls <- c('fb_rwi_mean',
                 'fb_rwi_mean_pop_wght',
                 'FB_pntr_15to49_female',
                 'FB_pntr_15to49_all')

afr_controls <- c('member_community',
                  'trpar',
                  'trtax',
                  'trgov',
                  'trlaw',
                  'trgen',
                  'trrel',
                  'trnei',
                  'tracq',
                  'railway_contact',
                  'explorer_contact',
                  'district_ethnic_frac',
                  'loc_ln_export_area')

cen_controls <- c('degree',
                  'betweenness',
                  'closeness')
```




We then merge datasets and create the country dummy:
```{r}
dat <- dhs %>% 
  select(pid,
         v021,
         strata,
         wt,
         GID_1 = gid_1,
         all_of(dhs_targets),
         all_of(dhs_controls)) %>% 
  left_join(sci %>% 
              select(GID_1 = user_loc,
                     all_of(sci_controls)),
            by = 'GID_1') %>% 
  left_join(hdi %>% 
              select(GID_1,
                     all_of(hdi_controls)),
            by = 'GID_1') %>% 
  left_join(wp %>% 
              drop_na(GID_1) %>% 
              select(GID_1,
                     all_of(wp_controls)),
            by = 'GID_1') %>% 
  left_join(fb %>% 
              select(GID_1,
                     all_of(fb_controls)),
            by = 'GID_1') %>% 
  left_join(afr %>% 
              select(GID_1,
                     all_of(afr_controls)),
            by = 'GID_1') %>% 
  left_join(sci_cen %>% 
              select(GID_1,
                     all_of(cen_controls)),
            by = 'GID_1') %>% 
  mutate(iso3 = substr(GID_1, 1, 3))
```

Here an overview of the variables we now have in our dataset:
```{r}
dim(dat)
names(dat)
```

A description of the variables can be found [here](https://drive.google.com/file/d/1vCgciS4_zMz6hs5SoRl8_5yxP5drHt1C/view?usp=sharing).

### Summary statistics

Let's look at summary statistics of a few handpicked 

```{r}
dat %>% 
  select(all_of(dhs_targets)) %>% 
  summary()
```

#### Preprocessing

Before we start looking at spatial autocorrelation and other modelling outcomes, we need to prepare our final dataset.

We center and scale SCI and WP features
```{r}
# Center and scale SCI variables
dat <- dat %>% 
  mutate(across(all_of(sci_controls), ~ scale(.x, scale = T)),
         across(all_of(wp_controls), ~ scale(.x, scale = T)),
         across(all_of(cen_controls), ~ scale(.x, scale = T))
         )
```


#### Modelling approaches

We have tried couple of different approaches, none produces really desirable results. Two main scenarios emerged:

Scenario 1: If we use 'Mean_friendship' as SCI measure, we get significant effects for 11 out of 33 health outcomes (most of them related to HIV knowledge, with quite strong effect sizes all in a positive direction: higher SCI -> more knowledge) when using the complex control setup incl. interaction effects.

Scenario 2: If we use 'Median_SCI_without_self' as SCI measure, we get significant effects for 21 out of 33 health outcomes (across topics, quite weak effects in different directions, which however "make sense") when using the HDI setup.

Both scenarios are not robust across samples or minor changes in specifications (e.g. adding/removing interaction effects)

Same observations hold true when using the general trust variable instead of the SCI.

Here a summary of the results for the first scenario:

```{r}

key_control <- c('Mean_SCI_with_Self')

basic_controls <- c(" +
              v104 +
              v012 +
              v025 +
              v106 +
              v243a +
              v270")

country_controls <- c("iso3")

additional_controls <- c("Mean_of_Night_Light +
                Mean_distance_to_major_rd +
                Mean_built_settlement_growth +
                FB_pntr_15to49_all +
                v243a:Mean_SCI_with_Self")

### Use of modern contraception <> Knowledge about modern contraception

i <- 'fp_use_mod'
j <- 'fp_know_mod'
interactions <- c(paste0(j,":",key_control))

temp <- dat %>% 
  select(v021,
           strata,
           wt,
           GID_1,
         all_of(i),
         all_of(j),
         all_of(dhs_controls), 
         all_of(sci_controls), 
         all_of(fb_controls), 
         all_of(wp_controls),
         iso3) %>% 
  drop_na

  DHSdesign <- svydesign(ids = temp$v021, strata=temp$strata, weights = temp$wt, nest=TRUE, data=temp)
  
  options(survey.adjust.domain.lonely=TRUE)
  options(survey.lonely.psu="adjust")

fp_use_mod_basic_fit <- svyglm(formula(paste(i,' ~',j,'+',
                      key_control,'+',
                      basic_controls,'+',
                      interactions)), 
                   family = quasibinomial(link="logit"),
                   design = DHSdesign)
fp_use_mod_additional_fit <- svyglm(formula(paste(i,' ~',j,'+',
                           key_control,'+',
                           basic_controls,'+',
                           additional_controls,'+',
                           interactions)), 
                   family = quasibinomial(link="logit"),
                   design = DHSdesign)
fp_use_mod_interaction_fit <- svyglm(formula(paste(i,' ~',j,'+',
                            key_control,'+',
                            basic_controls,'+',
                            additional_controls,'+',
                            country_controls,'+',
                            interactions)), 
                   family = quasibinomial(link="logit"),
                   design = DHSdesign)

tab_model(fp_use_mod_basic_fit, fp_use_mod_additional_fit, fp_use_mod_interaction_fit)

### Using condom with non-partner <> Knowledge about HIV transmission

i <- 'hk_cond_notprtnr'
j <- 'hk_knw_linear_index'
interactions <- c(paste0(j,":",key_control))

temp <- dat %>% 
  select(v021,
           strata,
           wt,
           GID_1,
         all_of(i),
         all_of(j),
         all_of(dhs_controls), 
         all_of(sci_controls), 
         all_of(fb_controls), 
         all_of(wp_controls),
         iso3) %>% 
  drop_na

  DHSdesign <- svydesign(ids = temp$v021, strata=temp$strata, weights = temp$wt, nest=TRUE, data=temp)
  
  options(survey.adjust.domain.lonely=TRUE)
  options(survey.lonely.psu="adjust")

hk_cond_notprtnr_basic_fit <- svyglm(formula(paste(i,' ~',
                      key_control,'+',
                      basic_controls,'+',
                      j,'+',
                      interactions)), 
                   family = quasibinomial(link="logit"),
                   design = DHSdesign)
hk_cond_notprtnr_additional_fit <- svyglm(formula(paste(i,' ~',
                           key_control,'+',
                           basic_controls,'+',
                           additional_controls,'+',
                           j,'+',
                           interactions)), 
                   family = quasibinomial(link="logit"),
                   design = DHSdesign)
hk_cond_notprtnr_interaction_fit <- svyglm(formula(paste(i,' ~',
                            key_control,'+',
                            basic_controls,'+',
                            j,'+',
                            additional_controls,'+',
                            country_controls,'+',
                            interactions)), 
                   family = quasibinomial(link="logit"),
                   design = DHSdesign)

tab_model(hk_cond_notprtnr_basic_fit, hk_cond_notprtnr_additional_fit, hk_cond_notprtnr_interaction_fit)

### Ever tested on HIV <> Knowledge about HIV transmission

i <- 'hk_test_ever'
j <- 'hk_knw_linear_index'
interactions <- c(paste0(j,":",key_control))

temp <- dat %>% 
  select(v021,
           strata,
           wt,
           GID_1,
         all_of(i),
         all_of(j),
         all_of(dhs_controls), 
         all_of(sci_controls), 
         all_of(fb_controls), 
         all_of(wp_controls),
         iso3) %>% 
  drop_na

  DHSdesign <- svydesign(ids = temp$v021, strata=temp$strata, weights = temp$wt, nest=TRUE, data=temp)
  
  options(survey.adjust.domain.lonely=TRUE)
  options(survey.lonely.psu="adjust")

hk_test_ever_basic_fit <- svyglm(formula(paste(i,' ~',
                      key_control,'+',
                      basic_controls,'+',
                      j,'+',
                      interactions)), 
                   family = quasibinomial(link="logit"),
                   design = DHSdesign)
hk_test_ever_additional_fit <- svyglm(formula(paste(i,' ~',
                           key_control,'+',
                           basic_controls,'+',
                           additional_controls,'+',
                           j,'+',
                           interactions)), 
                   family = quasibinomial(link="logit"),
                   design = DHSdesign)
hk_test_ever_interaction_fit <- svyglm(formula(paste(i,' ~',
                            key_control,'+',
                            basic_controls,'+',
                            j,'+',
                            additional_controls,'+',
                            country_controls,'+',
                            interactions)), 
                   family = quasibinomial(link="logit"),
                   design = DHSdesign)

tab_model(hk_test_ever_basic_fit, hk_test_ever_additional_fit, hk_test_ever_interaction_fit)

### Knowledge about modern contraception <> SCI

i <- 'fp_know_mod'

temp <- dat %>% 
  select(v021,
           strata,
           wt,
           GID_1,
         all_of(i),
         all_of(dhs_controls), 
         all_of(sci_controls), 
         all_of(fb_controls), 
         all_of(wp_controls),
         iso3) %>% 
  drop_na

  DHSdesign <- svydesign(ids = temp$v021, strata=temp$strata, weights = temp$wt, nest=TRUE, data=temp)
  
  options(survey.adjust.domain.lonely=TRUE)
  options(survey.lonely.psu="adjust")

fp_know_mod_basic_fit <- svyglm(formula(paste(i,' ~',
                      key_control,'+',
                      basic_controls)), 
                   family = quasibinomial(link="logit"),
                   design = DHSdesign)
fp_know_mod_additional_fit <- svyglm(formula(paste(i,' ~',
                           key_control,'+',
                           basic_controls,'+',
                           additional_controls)), 
                   family = quasibinomial(link="logit"),
                   design = DHSdesign)
fp_know_mod_interaction_fit <- svyglm(formula(paste(i,' ~',
                              key_control,'+',
                              basic_controls,'+',
                            additional_controls,'+',
                            country_controls)),
                   family = quasibinomial(link="logit"),
                   design = DHSdesign)

tab_model(fp_know_mod_basic_fit, fp_know_mod_additional_fit, fp_know_mod_interaction_fit)

### Knowledge about HIV transmission <> SCI

i <- 'hk_knw_linear_index'

temp <- dat %>% 
  select(v021,
           strata,
           wt,
           GID_1,
         all_of(i),
         all_of(dhs_controls), 
         all_of(sci_controls), 
         all_of(fb_controls), 
         all_of(wp_controls),
         iso3) %>% 
  drop_na

  DHSdesign <- svydesign(ids = temp$v021, strata=temp$strata, weights = temp$wt, nest=TRUE, data=temp)
  
  options(survey.adjust.domain.lonely=TRUE)
  options(survey.lonely.psu="adjust")

hk_knw_linear_index_basic_fit <- svyglm(formula(paste(i,' ~',
                      key_control,'+',
                      basic_controls)), 
                   family = quasibinomial(link="logit"),
                   design = DHSdesign)
hk_knw_linear_index_additional_fit <- svyglm(formula(paste(i,' ~',
                           key_control,'+',
                           basic_controls,'+',
                           additional_controls)), 
                   family = quasibinomial(link="logit"),
                   design = DHSdesign)
hk_knw_linear_index_interaction_fit <- svyglm(formula(paste(i,' ~',
                              key_control,'+',
                              basic_controls,'+',
                            additional_controls,'+',
                            country_controls)),
                   family = quasibinomial(link="logit"),
                   design = DHSdesign)

tab_model(hk_knw_linear_index_basic_fit, hk_knw_linear_index_additional_fit, hk_knw_linear_index_interaction_fit)

# Get final table
tab_model(fp_use_mod_interaction_fit, 
          # hk_cond_notprtnr_interaction_fit, 
          hk_test_ever_interaction_fit, 
          fp_know_mod_interaction_fit, 
          hk_knw_linear_index_interaction_fit)

# class(fp_use_mod_interaction_fit) <- "lmerMod"
# class(hk_cond_notprtnr_interaction_fit) <- "lmerMod"
# class(hk_test_ever_interaction_fit) <- "lmerMod"
# class(fp_know_mod_interaction_fit) <- "lmerMod"
# class(hk_knw_linear_index_interaction_fit) <- "lmerMod"
```





```{r message=FALSE, warning=FALSE}
basic_controls <- c('Mean_SCI_with_Self +
              v104 +
              v012 +
              v025 +
              v106 +
              v243a +
              v270')

country_controls <- c('iso3')

additional_controls <- c('Mean_of_Night_Light +
              Mean_distance_to_major_rd +
              Mean_built_settlement_growth +
              FB_pntr_15to49_all')

interactions <- c("v243a:Mean_SCI_with_Self")

ols_long_ia <- data.frame()

for(i in dhs_targets){
  
  temp <- dat %>% 
    select(v021,
           strata,
           wt,
           GID_1,
           all_of(i),
           all_of(dhs_controls), 
           all_of(sci_controls), 
           all_of(fb_controls), 
           # afr_controls,
           # all_of(hdi_controls), 
           all_of(wp_controls),
           all_of(cen_controls),
           iso3) %>% 
    drop_na

  DHSdesign <- svydesign(ids = temp$v021, strata=temp$strata, weights = temp$wt, nest=TRUE, data=temp)
  
  options(survey.adjust.domain.lonely=TRUE)
  options(survey.lonely.psu="adjust")
  
  summary_fit <- svyglm(formula(paste(i,'~',
                          basic_controls,'+',
                          additional_controls,'+',
                          country_controls,'+',
                          interactions)), 
                   family = binomial(link="logit"),
                   design = DHSdesign) %>% 
    summary
  
  ols_long_ia <- summary_fit$coefficients %>% 
    as.data.frame() %>% 
    select(estimate = Estimate, 'Pr(>|t|)') %>% 
    rename(p.value = 'Pr(>|t|)') %>% 
  rownames_to_column('term') %>% 
  filter(term == 'Mean_SCI_with_Self'|
         term == 'degree') %>% 
  select(estimate, p.value, term) %>% 
  mutate(outcome = i,
         significant_5p = ifelse(p.value <= 0.05, 'yes', 'no'),
         significant_1p = ifelse(p.value <= 0.01, 'yes', 'no')) %>% 
    bind_rows(ols_long_ia)
}

ols_long_ia %>% 
  arrange(desc(significant_5p))
```

```{r}
# basic_fit <- svyglm(formula(paste('hk_cond_notprtnr ~',basic_controls,'+',
#                           interactions)), 
#                    family = quasibinomial(link="logit"),
#                    design = DHSdesign)
# additional_fit <- svyglm(formula(paste('hk_cond_notprtnr~',basic_controls,'+',
#                           additional_controls,'+',
#                           interactions)), 
#                    family = quasibinomial(link="logit"),
#                    design = DHSdesign)

DHSdesign <- svydesign(ids = dat$v021, strata=dat$strata, weights = dat$wt, nest=TRUE, data=dat)

options(survey.adjust.domain.lonely=TRUE)
options(survey.lonely.psu="adjust")

fp_know_mod_basic_fit <- svyglm(formula(paste('fp_know_mod~',
                          basic_controls,'+',
                          additional_controls,'+',
                          country_controls)), 
                   family = quasibinomial(link="logit"),
                   design = DHSdesign)

hk_knw_linear_index_basic_fit <- svyglm(formula(paste('hk_knw_linear_index~',
                          basic_controls,'+',
                          additional_controls,'+',
                          country_controls)), 
                   family = quasibinomial(link="logit"),
                   design = DHSdesign)

fp_know_mod_interaction_fit <- svyglm(formula(paste('fp_know_mod~',
                          basic_controls,'+',
                          additional_controls,'+',
                          country_controls,'+',
                          interactions)), 
                   family = quasibinomial(link="logit"),
                   design = DHSdesign)

hk_knw_linear_index_interaction_fit <- svyglm(formula(paste('hk_knw_linear_index~',
                          basic_controls,'+',
                          additional_controls,'+',
                          country_controls,'+',
                          interactions)), 
                   family = quasibinomial(link="logit"),
                   design = DHSdesign)

tab_model(fp_know_mod_basic_fit, hk_knw_linear_index_basic_fit, fp_know_mod_interaction_fit, hk_knw_linear_index_interaction_fit)
```

Here the summary of results for the second scenario:

```{r message=FALSE, warning=FALSE}
controls_short <- c('Mean_SCI_with_Self +
                    HDI + 
                    hk_knw_comphsv +
                    hk_knw_comphsv:Mean_SCI_with_Self +
                    iso3')

temp_short <- dat %>% 
  select(pid, 
         v021,
         strata,
         wt,
         GID_1,
         all_of(dhs_targets),
         all_of(dhs_controls),
         all_of(sci_controls), 
         all_of(hdi_controls), 
         iso3) %>% 
  drop_na

DHSdesign_short <- svydesign(ids = temp_short$v021, strata=temp_short$strata, weights = temp_short$wt, nest=TRUE, data=temp_short)

options(survey.adjust.domain.lonely=TRUE)
options(survey.lonely.psu="adjust")

ols_short <- data.frame()

for(i in dhs_targets){
  summary_fit <- svyglm(formula(paste(i,'~',controls_short)), 
                   family = binomial(link="logit"),
                   design = DHSdesign_short) %>% 
    summary
  
  ols_short <- summary_fit$coefficients %>% 
    as.data.frame() %>% 
    select(estimate = Estimate, 'Pr(>|t|)') %>% 
    rename(p.value = 'Pr(>|t|)') %>% 
  rownames_to_column('term') %>% 
  filter(term == 'Median_SCI_without_Self') %>% 
  select(estimate, p.value) %>% 
  mutate(outcome = i,
         significant_5p = ifelse(p.value <= 0.05, 'yes', 'no'),
         significant_1p = ifelse(p.value <= 0.01, 'yes', 'no')) %>% 
    bind_rows(ols_short)
}

ols_short %>% 
  arrange(desc(significant_5p))
```

Let's look at the regression output of the two scenarios, exemplified using **hk_knw_risk_cond** ('Know you can reduce HIV risk by using condoms at every sex')

```{r}
fit_hk_knw_risk_cond_short <- svyglm(formula(paste('hk_knw_risk_cond~',controls_short)), 
                   family = binomial(link="logit"),
                   design = DHSdesign_short)

fit_hk_knw_risk_cond_long <- svyglm(formula(paste('hk_knw_risk_cond~',controls,'+ iso3')), 
                   family = binomial(link="logit"),
                   design = DHSdesign)

tab_model(fit_hk_knw_risk_cond_long, fit_hk_knw_risk_cond_short)
```


As expected, here the part of variation explained by the random intercept is even higher. Let's look at the residuals now.

```{r}
par(mfrow = c(1, 2))
plot(fitted(fit_hk_knw_risk_cond_long), resid(fit_hk_knw_risk_cond_long), col = 'green', main = 'Scenario 1')
plot(fitted(fit_hk_knw_risk_cond_short), resid(fit_hk_knw_risk_cond_short), col = 'blue', main = 'Scenario 2')
```

It seems that the random intercept largely reduces heterogeneity in the sample. We now look at the normality of the residuals via a qq-plot.

```{r}
par(mfrow = c(1, 2))
hist(resid(fit_hk_knw_risk_cond_long), 
     main = "Scenario 1", prob=TRUE, col = 'green')
lines(density(resid(fit_hk_knw_risk_cond_long)))
hist(resid(fit_hk_knw_risk_cond_short), 
     main = "Scenario 2", prob=TRUE, col = 'blue')
lines(density(resid(fit_hk_knw_risk_cond_short)))

```
